### 2021-03-23 ch02_scientific_background/scientific_background.tex
Added figure describing the land carbon uptake processes

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/sources_of_uncertainty.pdf}
  \caption[
    Schematic illustrating the importance of different sources of
    uncertainties in climate model projections and their evolution in time.
  ]{
    Schematic illustrating the importance of different sources of
    uncertainties in climate model projections and their evolution in time. (a)
    Time series of the anomaly of the decadal and global mean surface
    temperature relative to the period \range{1961}{1980}. The black line
    shows the historical observations with estimates of uncertainty from
    climate models (gray). The remaining colors show different sources of
    uncertainty in future climate projections: Natural variability (orange),
    climate response uncertainty (blue) and emission uncertainty (green)
    \autocite{Hawkins2009, Hawkins2010}. Climate response uncertainty can
    increase (b) in newer generations of climate models when a new process is
    discovered to be relevant or decrease (c) with additional model
    improvements and observational constraints.
    \IPCCReproducedFrom{Cubasch2013}{their FAQ 1.1, figure 1}.
  }
  \label{fig:02:sources_of_uncertainty}
\end{figure}

@@

Similar to many cloud processes, most carbon cycle--related processes need to
be parameterized in \acp{ESM} since they occur on spatial scales much smaller
than the typical grid cell sizes (see
\cref{subsec:02:numerical_climate_modeling}). For the terrestrial carbon cycle,
the major carbon exchange processes that need to be considered are
photosynthesis, respiration and disturbances, which connect the atmospheric
carbon reservoir and the land carbon reservoir. The latter mainly consists of
the vegetation biomass, litter and soil. The terrestrial carbon exchange
processes are commonly described with \ac{GPP}, \ac{NPP}, \ac{NEP} and
\ac{NBP}, which are all illustrated in \cref{fig:02:carbon_cycle_processes}.
\ac{GPP} describes the total carbon uptake of the vegetation by photosynthesis,
while \ac{NPP} refers to the net carbon gain of the plants after accounting for
autotrophic respiration ($\Ra{}$). \Ac{NEP} additionally considers
heterotrophic respiration ($\Rh{}$) and describes the carbon uptake/release of
the entire ecosystem. Finally, \ac{NBP} describes changes in the long-term
carbon storage of the terrestrial biosphere by including disturbances like
fires \autocite{Ciais2013}.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/sources_of_uncertainty.pdf}
  \caption[
    Schematic illustration of the importance of different sources of
    uncertainties in climate model projections and their evolution in time.
  ]{
    Schematic illustration of the importance of different sources of
    uncertainties in climate model projections and their evolution in time. (a)
    Time series of the anomaly of the decadal and global mean surface
    temperature relative to the period \range{1961}{1980}. The black line shows
    the historical observations with estimates of uncertainty from climate
    models (gray). The remaining colors show different sources of uncertainty
    in future climate projections: Natural variability (orange), climate
    response uncertainty (blue) and emission uncertainty (green)
    \autocite{Hawkins2009, Hawkins2010}. Climate response uncertainty can
    increase (b) in newer generations of climate models when a new process is
    discovered to be relevant or decrease (c) with additional model
    improvements and observational constraints.
    \IPCCReproducedFrom{Cubasch2013}{their FAQ 1.1, figure 1}.
  }
  \label{fig:02:sources_of_uncertainty}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/carbon_cycle_processes.pdf}
  \caption[
    Schematic illustration of the processes of the terrestrial carbon uptake.
  ]{
    Schematic illustration of the processes of the terrestrial carbon uptake.
    The \acf{GPP} describes the total carbon uptake of the vegetation by
    photosynthesis, while the \acf{NPP} refers to the net carbon gain of the
    plants after accounting for autotrophic respiration ($\Ra{}$). The
    \acf{NEP} additionally considers heterotrophic respiration ($\Rh{}$) and
    describes the carbon uptake/release of the entire ecosystem. Finally, the
    \acf{NBP} describes changes in the long-term carbon storage of the
    terrestrial biosphere by including disturbance losses ($\Ld{}$).
  }
  \label{fig:02:carbon_cycle_processes}
\end{figure}

Similar to many cloud processes, most carbon cycle--related processes need to
be parameterized in \acp{ESM} since they occur on spatial scales much smaller
than the typical grid cell sizes (see
\cref{subsec:02:numerical_climate_modeling}). For the terrestrial carbon cycle,
the major carbon exchange processes that need to be considered are
photosynthesis, respiration and disturbances, which connect the atmospheric
carbon reservoir and the land carbon reservoir. The latter mainly consists of
the vegetation biomass, litter and soil. The terrestrial carbon exchange
processes are commonly described with \ac{GPP}, \ac{NPP}, \ac{NEP} and
\ac{NBP}, which are all illustrated in \cref{fig:02:carbon_cycle_processes}.
\ac{GPP} describes the total carbon uptake of the vegetation by photosynthesis,
while \ac{NPP} refers to the net carbon gain of the plants after accounting for
autotrophic respiration ($\Ra{}$). \Ac{NEP} additionally considers
heterotrophic respiration ($\Rh{}$) and describes the carbon uptake/release of
the entire ecosystem. Finally, \ac{NBP} describes changes in the long-term
carbon storage of the terrestrial biosphere by including disturbances like
fires ($\Ld{}$).
